---
title: "United States Relative Populations and Changes"
author: "Fred Smith"
date: "Tuesday, June 07, 2016"
output: html_document
---

# Background

This site is my submission for the final project of the "Developing Data Products" course of the Data Science
Specialization in Coursera.

The primary goal was to learn interactive presentation tools such as Shiny, Slidify, and R Studio Presenter. These
tools are integrated with RStudio and commonly used by data scientists to publish their work.

The exercise was two-fold:

* Publish an interactive Shiny application and publish it to the shinyapps.io web site. The content for the exercise was left to the student, but the application had to have at least one input widget, some dynamic output rendered via R, and enough documentation that a novice user could use the application.

* Publish a presentation documenting the application and its findings.
        
Additionally, all project files are managed in github.com and published to public web sites (i.e., shinyapps.io and github.com)


# Structure

This project has two branches in Github. The current "gh-pages" branch contains the HTML files that were written by
hand and using RStudio (presentation) and are automatically published to the github.io hosting pages. The "master" branch contains the Shiny app files that were deployed to the Shiny server at shinyapps.io.

Consequently, there are several web pages that are all linked from the main github.io pages:

* http://fsmithus.github.io/DevelopDataProducts-Project/index.html - Index to project web sites.

* http://fsmithus.github.io/DevelopDataProducts-Project/USPopulation.html - Slide presentation describing the Shiny application.

* https://fsmith.shinyapps.io/master/ - Shiny application running dynamic pupulation study maps. The application may take a couple minutes to startup on the first visit.

* http://fsmithus.github.io/DevelopDataProducts-Project/README.html - This file, created as Rmd. Includes this information and the version information required to make this study reproduceable.

* https://github.com/fsmithus/DevelopDataProducts-Project/tree/master - Project master branch which contains the code for the Shiny application (i.e., ui.R and server.R).

* https://github.com/fsmithus/DevelopDataProducts-Project/tree/gh-pages - Project gh-pages branch which contains the static (compiled) project pages.


# Environment

The following packages were used to develop the web sites.

```{r message=FALSE}
library(maps)
library(mapproj)
library(maptools)
library(shiny)
library(shinyapps)
```

Versions were as shown below.

```{r}
sessionInfo()
```